\input cvmacros
\footline={\hss\number\pageno\hss}
\cvtitle
\cvheader{Contact}
\cvduelingcolumns{\cventry{Name}{Aaron Michael Silberstein}}{\cventry{Phone}{(312) 971--7347}}
\cvduelingcolumns{\cventry{Born}{April 4, 1984, Los Gatos, CA}}{\cventry{Skype (preferred chat)}{\tt simplicialset}}
\cvduelingcolumns{\cventry{Citizenship}{US}}{\cventry{E-mail}{\tt aaronmichaelsilberstein@gmail.com}}
\cvduelingcolumns{{\cvminiheaderfont Married}}{\cventry{Web}{\tt http://www.github.com/aaronmichaelsilberstein}}
\rheader{Education}
\cvdateline{{\bf Harvard University:} Ph.D. and A.M. in Mathematics}{2007--2012}
\cvsubline{Thesis: {\it Anabelian intersection theory}. Advisor: Prof.~Florian Pop, University of Pennsylvania.}
\cvdateline{{\bf Princeton University:} A.B. {\it magna cum laude\/} in Mathematics, Certificate in Linguistics}{2002--2007}
\cvdateline{{\bf PROMYS, Boston University:} Student}{Summers 2000, 2001}
\cvsubdescription{Program in Mathematics for Young Scientists: a selective summer program in advanced mathematics for high school students.}
\cvheader{Full-time Appointments}
\cvdateline{{\bf University of Chicago:} NSF Postdoctoral Fellow\kern-1pt/L.E. Dickson Instructor of Mathematics}{2014--2017}
\cvdateline{{\bf University of Pennsylvania:} Hans Rademacher Instructor of Mathematics}{2012--2014}
\cvheader{Visiting Positions}
\cvdateline{{\bf University of Chicago:} Department Visitor}{May 2014}
\cvdateline{{\bf Universit\`a degli Studi di Padova:} Visitor}{June 2013}
\cvdateline{{\bf National Taipei University of Technology:} Honorary Professor}{2012-2013}
\cvheader{Awards, Honors, and Grants}
\cvdateline{{\bf University of Chicago} FACCTS French Collaboration Grant}{2015--2017}
\cvsubline{For collaboration with French mathematicians. Amount: \$12,000 (used \$3,000).} 
\cvdateline{{\bf National Science Foundation} Postdoctoral Fellowship, Award No.~DMS--1400683}{2014--2017}
\cvsubline{Title: New Techniques in Anabelian Geometry and Applications to Algebraic Cycles}
\cvsubline{\phantom{Title: }and Rigidity in Complex Algebraic Geometry.}
\cvsubline{Mentor: Prof.~Madhav Nori, University of Chicago. Amount: \$150,000.}
\cvdateline{{\bf Simons Foundation} Travel Grant}{2013--2014}
\cvsubline{Amount: \$4,000.}
\cvdateline{{\bf National Science Foundation} Graduate Research Fellowship}{2008--2012}
\cvsubline{Provided stipend and teaching support for three years of graduate school research.}
\cvdateline{{\bf Department of Defense} National Defense Science and Engineering Graduate Fellowship}{2008--2011}
\cvsubline{Provided stipend and teaching support for three years of graduate school research.}
\cvdateline{{\bf Josephine de Karman Trust} Fellowship}{2006--2007}
\cvsubline{Endowed national prize established by aeronautics pioneer Theodore von K\'arm\'an.}
\cvdateline{{\bf Princeton University Department of Mathematics} Andrew H.~Brown Prize}{2006}
\cvsubline{Endowed prize for the best Junior undergraduate mathematics concentrator at Princeton University.}
\vfill\eject
\input cvresumecommonlangabout
\cvheader{References}
\cvline{Prof.~Florian Pop, University of Pennsylvania.}
\cvline{Prof.~Madhav Nori, University of Chicago.}
\cvline{Prof.~Benson Farb, University of Chicago.  Also for teaching.}
\cvline{Prof.~Jakob Stix, University of Heidelberg.}
\cvline{Prof.~Pierre Lochak, Universit\'e de Paris VI.}
\cvline{Prof.~Pierre D\`ebes, Universit\'e de Lille.}
\cvline{Prof.~Andrew Obus, University of Virginia.}
\cvline{Prof.~Henry Towsner, University of Pennsylvania.}
\cvline{Prof.~Glenn Stevens, Boston University.}
\vfill
\eject
\cvheader{Papers in Pure Mathematics}
\cvnewlist
\cvitemline{{\it Anabelian Intersection Theory.}  PhD Thesis, Harvard University.}
\cvitemline{{\it An Anabelian Theorem for Function Fields over $\overline{\bf Q}$}. Submitted to the {\it Israel Journal of Mathematics}.}
\cvitemsubline{In revision.  Available on the ArXiv at {\tt http://arxiv.org/abs/1211.4608}}
\cvitemline{{\it Families of Disjoint Divisors on Varieties}, with Fedor Bogomolov and Alena Pirutka.}
\cvitemsubline{Reference: European Journal of Mathematics, 2016, DOI 10.1007/s40879--016--0109--1.}
\cvline{\it Details on work in progress available on request.}
\cvheader{Invited Talks in Pure Mathematics}
\cvdateline{{\bf University of Western Ontario,} Algebra Seminar}{September 2017}
\cvdateline{{\bf Wayne State University,} Department Colloquium}{April 2017}
\cvdateline{{\bf Columbia University,} Algebraic Geometry Seminar}{April 2016}
\cvdateline{{\bf University of Virginia,} Algebraic Geometry Seminar}{February 2016}
\cvdateline{{\bf University of Virginia,} Undergraduate Math Club}{February 2016}
\cvdateline{{\bf AMS Sectional Meeting} at Rutgers University}{November 2015}
\cvsubline{Special session on ``Advances in Valuation Theory''}
\cvdateline{{\bf New York University,} Algebraic Geometry Seminar}{November 2015}
\cvdateline{{\bf Purdue University,} Algebraic Geometry Seminar}{September 2015}
\cvdateline{{\bf Mathematisches Forschungsinstitut Oberwolfach}}{October 2014}
\cvsubline{Workshop on ``Valuation Theory and its Applications''}
\cvdateline{{\bf Universit\'e de Lille,} Number theory days}{June 2014}
\cvdateline{{\bf University of California, Berkeley,} Number Theory Seminar}{March 2014}
\cvdateline{{\bf University of Arizona,} Number Theory Seminar}{March 2014}
\cvdateline{{\bf The Ohio State University,} Algebraic Geometry Seminar}{March 2014}
\cvdateline{{\bf Vietnam Institute for Advanced Study in Mathematics}}{July 2013}
\cvdateline{{\bf Mathematisches Forschungsinstitut Oberwolfach}}{June 2013}
\cvsubline{Workshop on ``The Arithmetic of Fields''}
\cvdateline{{\bf Universit\`a degli Studi di Padova,} Research Talk}{June 2013}
\cvdateline{{\bf Stony Brook University,} Algebraic Geometry Seminar}{May 2013}
\cvdateline{{\bf \.IMBM, Bo\u gazi\c ci University,} week-long lecture series}{December 2012}
\cvdateline{{\bf University of Chicago,} Geometry/Topology Seminar}{November 2012}
\cvdateline{{\bf Tel Aviv University,} Number Theory Seminar}{June 2012}
\cvdateline{{\bf University of Pennsylvania,} Number Theory Seminar}{April 2012}
\cvdateline{{\bf Montr\'eal} Number Theory Seminar}{March 2012}
\cvsubline{Biweekly seminar for McGill University, Concordia University and Universit\'e de Montr\'eal}
\cvdateline{{\bf Boston University,} Number Theory Seminar}{December 2011}
\cvdateline{{\bf Harvard University,} Number Theory Seminar}{November 2011}
\cvheader{Academic Service}
\cvdateline{{\bf Drexel University:} Served on candidacy committee for Timothy Hayes at }{September 2013}
\cvdateline{{\bf University of Chicago:} Organizer, Algebraic Geometry Seminar}{2014--present}
\vfill\eject
\cvheader{Teaching Activities}
\cvdateline{{\bf University of Chicago:} Linear Algebra, Math 20250}{Fall 2016}
\cvdateline{{\bf University of Chicago:} Abstract Algebra, Math 255}{Winter 2015}
\cvsubdescription{These two courses were essentially identical: abstract linear algebra and introduction to proofs with algebraic structures for math majors.  I taught two sections of each, held office hours, and managed TA's.}
\cvdateline{{\bf University of Chicago:} Young Scholars Program}{Winter 2015}
\cvsubdescription{Taught an introduction to elementary number theory as weekend enrichment for interested Chicago high school students under the aegis of the Young Scholar's Program, and managed the undergraduates who assisted with the program.}
\cvdateline{{\bf University of Pennsylvania:} Proving Things: Algebra, Math 203}{Spring 2014}
\cvsubdescription{Taught one section of introduction to proof with formal logic for students who think they might want to major in mathematics.  Managed one graduate student TA.}
\cvdateline{{\bf University of Pennsylvania:} ``Active Learning'' Calculus, Math 104 (Calculus I)}{Fall 2014}
\cvsubdescription{Designed this course Prof.~Annalisa Crannell of Franklin \& Marshall College, Prof.~Robin Pemantle of the University of Pennsylvania, and Prof.~Camelia Pop, now at the University of Minnesota.  I taught one section and served as course head for two sections of the flipped classroom, worksheet-based, second-semester undergraduate calculus course we developed.  I managed two graduate student TA's.}
\cvdateline{{\bf University of Pennsylvania:} Undergraduate Algebra, Math 370}{Fall 2014}
\cvsubdescription{Undergraduate algebra course for math majors.}
\cvdateline{{\bf Ho Chi Minh City University of Science:} Quadratic Reciprocity}{Summer 2013} % To do: get VNese diacritics right and put them here!
\cvsubdescription{Taught an introductory course on a cyclotomic proof of quadratic reciprocity to advanced undergraduates.}
\cvdateline{{\bf University of Pennsylvania:} Linear Algebra}{Spring 2013}
\cvsubdescription{Taught two sections of a linear algebra course for engineers and Wharton students.  Managed two TA's.}
\cvdateline{{\bf Universit\`a degli Studi di Padova:} Anabelian Geometry}{Summer 2013}
\cvsubdescription{Taught a month-long course on anabelian geometry and abstract Galois theory to graduate students in Padua.}
\cvdateline{{\bf AUIA Summer Program, Taipei:} Linear Algebra and Multivariable Calculus}{July 2012}
\cvsubdescription{Taught two short courses, managed three undergraduate TA's.}
\cvdateline{{\bf Harvard University:} Math M}{2008--2010}
\cvsubdescription{Coordinated and documented Inquiry-Based Learning (IBL) components of Math M, the hybrid pre-calculus/calculus course at Harvard.  I worked in small groups with students in the class, and trained undergraduates to guide student ``workshops'' using IBL methods.  I also participated heavily in the development of the curriculum related to this component of the course.  Managed 5--10 undergraduate TA's each semester.}
\cvdateline{{\bf PROMYS:} Research supervisor}{Summers 2008, 2009}
\cvsubdescription{Supervised high school students' research projects at PROMYS.}
\cvdateline{{\bf Harvard University:} Summer Tutorial on the Model Theory of Fields}{Summer 2008}
\cvsubdescription{Designed and taught a summer course for undergraduate math majors.}
\cvdateline{{\bf Harvard University:} Math Question Center}{Spring 2008}
\cvsubdescription{Supervised drop-in help center, encouraging students to work in groups and teach each other material.}
\cvdateline{{\bf PROMYS:} Counselor}{Summers 2003-2007}
\cvsubdescription{Each summer, was responsible for grading the problem sets of four high school students and organizing and presenting in mathematics seminars for fellow counselors.}
\end
\section{Teaching Activities}
\section{Miscellaneous}
Languages spoken (in decreasing competence): English (native); Romanian (fluent); Bosnian/Croatian/Serbian (conversational); French, Spanish (conversational); Hungarian, Italian (reading/writing); Russian (reading).
\section{References}
\begin{enumerate}
\end{enumerate}
In pure mathematics, I am interested in modern Galois theory, algebraic geometry, and geometric group theory in general, and I focus most of my attention on making rigidity theorems explicit.  I have proved new birational rigidity theorems for algebraic varieties by introducing a new class of geometric techniques, called anabelian intersection theory.  I am working on extending these results, understanding their applications and making them effective and computationally efficient.  I am also working on some projects in model theory and fundamental Galois theory.

\end{document}
